Brownian Dynein Model

### 2016-01-12 latex/paper.tex
add garbage paper for code-related diagrams

\documentclass[11pt, landscape]{article}

@@

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bb} &= 0 \\
  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
\end{align}

\begin{align}
  Y_{bb} &= 0 \\
  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bb} &= 0 \\                                                               
  \dot{Y}_{bm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bb} &= 0 \\
  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
\end{align}

%Unnecessary section commented out
\begin{comment}
\section{Expanded Brownian Equations}

\begin{align}
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

\section{System after Subtracting out Angular Velocity Terms}
This is the system after subtracting equations from each other to eliminate some angular velocity terms.\\

\begin{align}
  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) - R_{xml} \\
  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) - R_{xt } \\
  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) - R_{yml}\\
  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) - R_{yt } \\
  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) - R_{ymr} 
\end{align}
\end{comment}

\section{System of Equations}
This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\

\begin{align}  
  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + R_{xt } \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + R_{yt } \\
  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

\section{System after Addition}
By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(X_{bm} - X_{bb}) =
\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Ax}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{bm}) =
\dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Bx}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{ft}(X_{fm} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Cx}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) = 
\dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Dx}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(Y_{bm} - Y_{bb}) =
\dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Ay}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{bm}) =
\dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:By}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{ft}(Y_{fm} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Cy}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) = \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Dy}
\end{equation}%Fix'd

\section{Creating Angular Velocity Matrix}

Our goal is to take the above system of equations and put it in matrix form:

\begin{align}
  A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} &= X_1 \\
  B_1\dot{\Theta}_{bb} + B_2 \dot{\Theta}_{bm} + B_3 \dot{\Theta}_{fm} + B_4 \dot{\Theta}_{fb} &= X_2 \\
  C_1\dot{\Theta}_{bb} + C_2 \dot{\Theta}_{bm} + C_3 \dot{\Theta}_{fm} + C_4 \dot{\Theta}_{fb} &= X_3 \\
  D_1\dot{\Theta}_{bb} + D_2 \dot{\Theta}_{bm} + D_3 \dot{\Theta}_{fm} + D_4 \dot{\Theta}_{fb} &= X_4 \\
\end{align}

This will allow us to perform a matrix solution for the angular velocities. $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s. The above system of equations has four lambda terms: $\lambda_{bs}, \lambda_{bt}, \lambda_{ft}$ and $\lambda_{bs}$. Each term is present in two equations. We will use this redundancy to eliminate the lambda terms and create the above matrix.

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} = X_1$\\

We start by dividing out the position terms in Equations (\ref{eq:Ax}) and (\ref{eq:Ay}) to make their LHSs identical.

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs} =
\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{bm} - X_{bb})}
\end{multline}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs} =
\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{bm} - Y_{bb})}
\end{multline}

We then equate them.

\begin{multline}
\Big(\dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{bm} - Y_{bb}) = \\
\Big( \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} \\
+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{bm} - X_{bb})
\end{multline}

Then we group like terms for clarity.

\begin{multline}
\Big(\dot{X}_{bb} + \dot{X}_{bm} + \dot{X}_{t } + \dot{X}_{fm} 
- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} \\
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
\Big(\dot{Y}_{bb} + \dot{Y}_{bm} + \dot{Y}_{t } + \dot{Y}_{fm}
+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} \\
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
\end{multline}

We then expand all the $\dot{X}$ terms using their definitions from the Cartesian Velocities section above.

\begin{multline}
\Big(
- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb}
- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm}\\
- L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
\Big(
+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb}
+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm}\\
+ L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
\end{multline}

Then we group together the like terms from the expansion.

\begin{multline}
\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bb})) = \\
\Big(4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
\end{multline}

We then bring all the angular velocity terms to one side and all the force terms to the other side.

\begin{multline}
\Big(- 4L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm}
+ 2L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\sin(\Theta_{bb}))\\
\Big(-4L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} - 3L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm}
+ 2L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}\Big)(L_s\cos(\Theta_{bb}))= \\
\Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bb}))
+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(L_s\sin(\Theta_{bb}))
\end{multline}

We then distribute the $L_s\sin(\Theta_{bb})$ and $L_s\cos(\Theta_{bb})$ terms into the expression.

>>>>

\documentclass[11pt]{article}

@@

Hello world

\includegraphics[width=3cm]{../figures/code-bothbound}
